SAT Competition 2020\tnoteref{title}

### 2021-06-04 paper/main.tex
minor things in intro

From what was once mainly the archetypal intractable (in particular NP-complete) problem, propositional satisfiability 
(or Boolean satisfiability, SAT) has flourished, in practice, into a success story of modern computer science~\cite{DBLP:series/faia/2009-185}.
This is due to advances in SAT solvers, i.e., implementations of decision procedures for SAT, which today form a 
central computational tool for solving real-world problem instances of various kinds of NP-hard search and optimization problems.
With standardized input formats, readily-available APIs for incremental applications,
and certified proof logging and checking capabilities, applications of SAT solver technology
have branched from the first breakthrough applications in automated planning, test pattern generation and hardware verification
to thousands of different application settings.

The success of SAT would not be possible without the persistent efforts of the SAT community to further develop the performance and robustness
of SAT solvers. The SAT Competition series, with a history dating back to the early 90s, aims to support and provide further incentives 
for maintaining and furthering this progress. Organized yearly as an international open event, the SAT competitions (and their variants
in the form of SAT Races and SAT Challenge)~\cite{DBLP:journals/amai/SimonBH05,DBLP:conf/sat/BerreS03,DBLP:conf/sat/BerreS04,DBLP:journals/aim/JarvisaloBRS12,DBLP:journals/ai/BalintBJS15,DBLP:conf/aaai/BalyoHJ17,DBLP:journals/jsat/HeuleJS19}
 have a consistent track record of receiving tens of solver submissions yearly, submitted
by the community at large for obtaining a snapshot of the current state-of-the-art in practical SAT solving. Alongside participating solvers,
the competition invites through open calls submissions of benchmark instances representing, in particular, new interesting applications 
scenarios of SAT solvers. Indeed, in addition to evaluating recently developed solvers, an important aspect of the SAT competition series is
to collect on a yearly basis new benchmark sets, consisting of instances from various different application settings, which together with benchmark sets from previous years constitute a standard dataset for use in research papers and SAT solver development.

This article focuses on the 2020 instantiation of the SAT competitions. 
To this end, we provide
a detailed account of SAT Competition 2020 in terms of organizational details, competition tracks,
participating solvers, benchmarks, and the empirical results from the competition.
In terms of competition tracks, two new tracks, namely the cloud track and an application-specific track, where introduced in 2020,
in addition to the already earlier established main, parallel, and incremental tracks; we
provide motivation and the new organizational details for both of these new tracks.
In terms of solvers, we provide an overview of solving strategies and other details implemented in the top-performing solvers
from the competition, complementing the individual solver descriptions available in the 2020 competition proceedings~\cite{SC2020}.
 As for benchmarks, we describe how the 2020 benchmark sets were constructed for each of the competition tracks, with 
an overview of the benchmarks contributed to the 2020 competition.
In terms of empirical results we provide further analysis on the results going beyond the standard rankings provided
on the SAT competition web pages.\footnote{\url{https://satcompetition.github.io/2020/}}
Finally, we also provide a discussion on lessons learned and ideas for future editions of SAT competitions.

The rest of this article is organized as follows. 
We start by providing an overview on the competition, including details on and motivations for the several
competition tracks, the rules and other technical requirements of the competition, the ranking schemes used
in evaluating the competing solvers, 
and the computing environments used for executing the competition
(Section~\ref{sec:overview}).
We then provide an overview of the benchmark sets used in evaluating the solvers, including their origins and the selection
process used for constructing the sets (Section~\ref{sec:instances}).
In Section~\ref{sec:results} we provide an overview of the competition results %together with a survey on the
followed by a survey on 
the solving strategies implemented distinctly in the top-ranking solvers in Section~\ref{sec:winners}. 
Going considerably beyond the plain competition rankings, in Section~\ref{sec:analysis}, we provide an in-depth analysis of the competition 
data from different perspectives, including correlation analysis of runtime performance of solvers and marginal contributions
of individual solvers to the ``virtual best solver'' and 
portfolios constructed from the competing solvers.
The article is concluded with future prospects in Section~\ref{sec:conclusion}.

@@

Benchmark instances selection in SAT Competition  2020 was realized using GBD Tools\footnote{\url{https://pypi.org/project/gbd-tools/}} which is a tool-chain for maintenance and distribution of benchmark instances and instance attributes~\cite{Iser:2018:GBD}.
Using the concept of instance identification via GBD Hash, which is the hash-sum of the unpacked and normalized DIMACS file, GBD Tools provide utilities to query for instances with desired properties, e.g., instance author, family and result.
Instance attributes are maintained in publicly available databases, which provide information about all instances used in SAT Competitions since 2006.\footnote{\url{https://gbd.iti.kit.edu}} 
Benchmark instance identification also simplifies the distribution of instances via the GBD Server.\footnote{\url{https://gbd.iti.kit.edu/file/<gbd-hash>}}

@@

The ``Bring Your Own Benchmarks'' (BYOB) rule, first  established in SAT Competition 2017~\cite{SC2017}, was again followed
in 2020.
By this rule, solver authors are required to submit $20$ new benchmark instances in order to participate in the competition. At least $10$ of these instances are required to be ``interesting'', meaning that the standard Minisat SAT solver
must need more than a minute to solve it and the authors own solver does not run into a timeout for the instance.

As can be seen in Table~\ref{tab:families}, $27$ authors contributed a set of $1260$ previously unseen benchmark instances from a wide range of different instance families. 
In order to create a balanced set of 300 new benchmarks and 100 old benchmarks, i.e., instances seen in previous competitions, we executed the following steps of \emph{rule-based randomization}.

@@

Backbone variables are defined to be those variables which have the same value in all models of a given instance~\cite{Monasson:1999,Janota:2015:Backbones}. 
The application \textsf{genipabones} incrementally determines backbone variables in a given satisfiable SAT instances using the dual rail encoding~\cite{Balyo:2015:SATRace}.
We selected $50$ of the smallest and easiest satisfiable instances from previous SAT competitions to evaluate solver performance with this application.

@@

The IPASIR interface facilitates the integration of SAT Solvers into incremental applications. 
In contrast to benchmarking with instances given in DIMACS CNF, there are only a couple of benchmark applications available for the Incremental track which are also less organized. 
This calls for the creation of a more diverse and organized repository of applications for incremental SAT solvers. 
Proper benchmarking and new tools for testing incremental SAT solvers can help solver authors to deal with the more complex use-case.\footnote{\url{https://github.com/fkutzner/IncrementalMonkey}}

>>>>

From what was once mainly the archetypal intractable (in particular NP-complete) problem, propositional satisfiability 
(or Boolean satisfiability, SAT) has flourished into a success story of modern computer science~\cite{DBLP:series/faia/2009-185}.
This is due to advances in SAT solvers, i.e., implementations of decision procedures for SAT, which today form a 
central computational tool for solving real-world problem instances of various kinds of NP-hard search and optimization problems.
With standardized input formats, readily-available APIs for incremental applications,
and certified proof logging and checking capabilities, applications of SAT solver technology
have branched from the first breakthrough applications in automated planning, test pattern generation and hardware verification
to thousands of different application settings.

The success of SAT would not be possible without the persistent efforts of the SAT community to further improve the performance and robustness
of SAT solvers. The SAT Competition series, with a history dating back to early 90s, aims to support and provide further incentives 
for maintaining this progress. Organized yearly as an international open event, the SAT competitions (and their variants
in the forms of SAT Races and a SAT Challenge)~\cite{DBLP:journals/amai/SimonBH05,DBLP:conf/sat/BerreS03,DBLP:conf/sat/BerreS04,DBLP:journals/aim/JarvisaloBRS12,DBLP:journals/ai/BalintBJS15,DBLP:conf/aaai/BalyoHJ17,DBLP:journals/jsat/HeuleJS19}
 have a consistent track record in receiving tens of solver submissions yearly, submitted
by the community at large for obtaining a snapshot of the current state-of-the-art in practical SAT solving. Alongside participating solvers,
the competition invites through open calls submissions of benchmark instances representing, in particular, new interesting applications 
scenarios of SAT solvers. Indeed, in addition to evaluating recently developed solvers, an important aspect of the SAT competition series is
to collect on a yearly basis new benchmark sets, consisting of instances from various different application settings, which together with benchmark sets from previous years constitute a standard dataset for use in research papers and SAT solver development.

This article focuses on the 2020 instantiation of the SAT Competitions. 
To this end, we provide
a detailed account of SAT Competition 2020 in terms of organizational details, competition tracks,
participating solvers, benchmarks, and the empirical results from the competition.
In terms of competition tracks, two new tracks, namely the cloud track and an application-specific track, where introduced in 2020,
in addition to the already earlier established main, parallel, and incremental tracks; we
provide motivation and the new organizational details for both of these new tracks.
In terms of solvers, we provide an overview of solving strategies and other details implemented in the top-performing solvers
from the competition, complementing the individual solver descriptions available in the 2020 competition proceedings~\cite{SC2020}.
 As for benchmarks, we describe how the 2020 benchmark sets were constructed for each of the competition tracks, with 
an overview of the benchmarks contributed to the 2020 competition.
In terms of empirical results we provide further analysis on the competition results, going beyond the standard rankings provided
on the SAT competition web pages.\footnote{\url{https://satcompetition.github.io/2020/}}
Finally, we also provide a discussion on lessons learned and ideas for future editions of SAT competitions.

The rest of this article is organized as follows. 
We start by providing an overview on the competition, including details on and motivations for the several
competition tracks, the rules and other technical requirements of the competition, the ranking schemes used
in evaluating the competing solvers, 
and the computing environments used for executing the competition
(Section~\ref{sec:overview}).
We then provide an overview of the benchmark sets used in evaluating the solvers, including their origins and the selection
process used for constructing the sets (Section~\ref{sec:instances}).
In Section~\ref{sec:results} we provide an overview of the competition results %together with a survey on the
followed by a survey on 
the solving strategies implemented distinctly in the top-ranking solvers in Section~\ref{sec:winners}. 
Going considerably beyond the plain competition rankings, we provide in Section~\ref{sec:analysis}, an in-depth analysis of the competition 
data from different perspectives, including correlation analysis of runtime performance of solvers and marginal contributions
of individual solvers to the ``virtual best solver'' and 
portfolios constructed from the competing solvers.
The article is concluded with future prospects in Section~\ref{sec:conclusion}.

@@

For data-driven selection and distribution of benchmark instances, we use GBD~Tools\footnote{\url{https://pypi.org/project/gbd-tools/}} which facilitates querying for instances with desired properties, e.g., instance author, family, result or solver-runtime~\cite{Iser:2018:GBD}. 
We also run GBD~Tools on a server to distribute benchmark instances and attribute databases.\footnote{\url{https://gbd.iti.kit.edu}}

@@

The ``Bring Your Own Benchmarks'' (BYOB) rule, first  established in SAT Competition 2017~\cite{SC2017}, was again followed
in 2020.
By this rule, solver authors are required to submit $20$ new benchmark instances in order to participate in the competition. At least $10$ of these instances are required to be ``interesting'', meaning that \solver{Minisat} must not solve it in less than one minute.

As can be seen in Table~\ref{tab:families}, $27$ authors contributed a set of $1260$ previously unseen benchmark instances from a wide range of different instance families. 
In order to create a balanced set of 300 new benchmarks and 100 old benchmarks, i.e., instances from previous competitions, we executed the following steps of \emph{rule-based randomization}.

@@

Backbone variables~\cite{Monasson:1999,Janota:2015:Backbones} are variables which take the same value in all models of a given SAT instance.
The application \textsf{genipabones} incrementally determines backbone variables in a given satisfiable SAT instances using the dual rail encoding~\cite{Balyo:2015:SATRace}.
We selected $50$ of the smallest and easiest satisfiable instances from previous SAT competitions to evaluate solver performance with this application.

@@

The IPASIR interface facilitates the integration of SAT solvers into incremental applications. 
In contrast to benchmarking with instances given in DIMACS CNF, there are only a couple of benchmark applications available for the Incremental track which are also less organized. 
This calls for the creation of a more diverse and organized repository of applications for incremental SAT solvers. 
Proper benchmarking and new tools for testing incremental SAT solvers can help solver authors to deal with the more complex use-case.\footnote{\url{https://github.com/fkutzner/IncrementalMonkey}}
